# Loading functions: load.csv(), load.data.frame()

Both of the loading functions operate identically, what differs is the way the function receives the event log as input.
When using the **load.csv** function, a.csv file is requested as input; however, when using the **load.data.frame** function, the event log provided as input must be a data frame.

The following inputs must be given and are mandatory for the correct loading:

 -	**IDName**: name of EL column for case ID 
 -	**EVENTName**: name of EL column for Event label
 -	**dateColumnName**: name for the Date column, 
 -	**format.column.date** = date format (default:"_%d/%m/%Y %H:%M:%S"_) 

If the load. csv function is performed, it is important to enter details regarding the format in which the event log file is saved:

 -	**quote**: default _" " "_
 -	**sep** : default _","_

The loading functions offer additional functionality, which the user may specify using the following fields:

 -	**convertUTF**: Boolean;
 -	**suppress.invalid.date** : Boolean, if true suppress invalid date;
 -	**guessDataFormat**: Boolean, if true allows to automatically calculate the date format.
 
Let's try using the functions to load an EventLog:
```{r, echo=FALSE, eval=FALSE}
library(pMineR)
objDL<-dataLoader()
```

```{r eval=TRUE}

EL<-read.csv("EventLog1.csv",header = T,sep = ",",quote = "")

head(EL)

```

```{r eval=FALSE}

objDL$load.csv(nomeFile = "EventLog1.csv",
               IDName = "ID",
               EVENTName = "Event",
               dateColumnName = "Date",
               sep  = ",",
               quote = "",
               format.column.date = "%Y-%m-%d")

objDL$load.data.frame(mydata = EL,
                      IDName = "ID",
                      EVENTName = "Event",
                      dateColumnName = "Date",
                      format.column.date = "%Y-%m-%d")
```
 

Once the event log is loaded, the Data Loader class will create structured data that can be accessed using the _getData()_ function.

```{r eval=FALSE}

obj.out<-objDL$getData()
```

