# Word translation and grouping functions: applyFilter() and getTranslation() 
```{r, echo=FALSE, eval=TRUE, results= 'hide',warning=FALSE, message=FALSE}

library(pMineR)
objDL<-dataLoader()

objDL$load.csv(nomeFile = "EventLog1.csv", IDName = "ID",EVENTName = "Event",dateColumnName = "Date",sep  = ",",quote = "",format.column.date = "%Y-%m-%d")

obj.out<-objDL$getData()
obj.out$arrayAssociativo
obj.out$MMatrix
obj.out$pat.process[["1"]]


```

**applyFilter()**  function allows filtering on the Event Log based on:

 -	Specific event: using “array.events.to.remove” input to explicit the label of the events to remove;
 -	Specific patient: using “array.pazienti.to.keep” or “array.pazienti.to.remove” to explicit the ID of cases to keep (or to remove);
 -	Specific attribute values: using “remove.events.by.attribute.name” input (or “remove.patients.by.attribute.name”) to remove event (or cases) according to the value (“by.arr.attribute.value”) of a specific attribute. 
 
The function could give different output based on the value for the **“whatToReturn”** input: 

 -	whatToReturn= _"itself"_ will return DataLoader object itself;
 -	whatToReturn= _“csv”_ will return a new modified Event Log as a new data frame
 -	whatToreturn= _“dataLoader”_ will return a new DataLoader object 
 
 Suppose we want to remove all rows that correspond to "Biopsy" events:
 
```{r,results= 'hide',warning=FALSE, message=FALSE}
new_EL<-objDL$applyFilter(array.events.to.remove = c("Biopsy"),whatToReturn = "csv")
```
```{r}
unique(new_EL$Event)
```
 
 

**getTransalation()** function allows to modify event label according to a new dictionary that the user may upload using the **add.Dictionary()** function. 

addDictionary() function adds dictionaries in order, afterward, to translate or group some event name. the new dictionary should be a csv file, consisting of two columns: the first one for the original event labels and the second one for the new labels. The addDictionary function will require as input:

 -	Dictionary file name;
 -	Separator (default “,”)
 -	dict.name: name for the new dictionary (default “main”)
 -	column.event.name: name of the first column of the csv file (referred to the actual event Label)
 
Once the new dictionaries are loaded you can apply them using the getTranslation(), which has the following inputs:

 -	dict.name:  name of the dictionary to use
 -	column.name: dictionary column name containing the new labels
 -	toReturn: for explicit the kind of the desired output (see whatToReturn output of applyFilter() function)
 
Let's try using the methods just listed to change the event label "MedicalVisit" to "Medical Visit". To do so we will use the following dictionary:
```{r}
read.csv("newDictionary.csv",sep = ";",header = T,quote = "")
```

At first we have to load the new dictionary with the addDictionary function:

```{r, echo=TRUE, eval=TRUE, results= 'hide',warning=FALSE, message=FALSE}
objDL$addDictionary(fileName = "newDictionary.csv",
                    sep = ";",
                    dict.name = "dict1",
                    column.event.name = "oldLabel")

```

Then using getTranslation, the dictionary can be used ()
```{r,echo=TRUE, eval=TRUE, results= 'hide',warning=FALSE, message=FALSE}
newEL<-objDL$getTranslation(column.name = "newLabel",dict.name = "dict1",toReturn = "csv")

```

```{r}
unique(newEL$Event)
```

